Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-04-02 bbbq_article.tex
Spellcheck
Updates from Overleaf

In our previous work, we found that the observed pattern can be
explained from the hydrophobicity of the MHC-I binding 
cleft (\cite{bianchi2017}), we validated.
Here we do the same analysis for MHC-II 
\richel{Really need to do? If yes, explain the analysis here}.

@@

We next wondered if the over-representation of TMH-derived peptides would also be present for MHC-II. 
Figure \ref{fig:bbbq_1_smart_results} shows the percentages of MHC-II epitopes predicted to be overlapping 
with TMHs for our human, viral and bacterial proteomes.
See supplementary table \ref{tab:tmh_binders_mhc2} 
for the TMH and epitope counts.
We predict that TMH-derived peptides are also over-presented in most MHC-II haplotypes, and this over-presentation seems even more pronounced than for MHC-I. 
\richel{
  Decide in meeting: 
  showing how general our finding is (as it is explained by hydrophobicity)
  is important. See \url{https://github.com/richelbilderbeek/bbbq_article/issues/192}
}
Similar to our previous results with MHC-I, we predicted that the extent to which TMH-derived
epitopes are presented by each MHC-II haplotype is similar for the human, bacterial and viral proteome.

@@

To verify if the previous and the current method give rise to
notable difference, we show a side-by-side comparison
in figures \ref{fig:bianch_et_al_2017_1a} and \ref{fig:bilderbeek_et_al_2021_1a}.
The figures that haplotypes that over-present or under-present TMH-derived epitopes,
do so in both studies. The extent to which TMH-derived eptitopes are
presented, however, is more extreme in our current setup.

>>>>

In our previous work, we found that the observed pattern can be
explained from the hydrophobicity of the MHC-I binding cleft (\cite{bianchi2017}).
Here we do a similar analysis, by correlating the percentage of TMH-derived
epitopes presented versus the mean hydrophobicity of all presented
peptides. From these points, we derive a linear trendline and measure
the $R^2$, where $R^2$ is the proportion of the correlation explained by
the assumed linear relation.

@@

We next wondered if the over-representation of TMH-derived peptides would also be present for MHC-II. 
Figure \ref{fig:bbbq_1_smart_results} shows the percentages of MHC-II epitopes predicted to be overlapping 
with TMHs for our human, viral and bacterial proteomes.
See supplementary table \ref{tab:tmh_binders_mhc2} 
for the TMH and epitope counts.
We predict that TMH-derived peptides are also over-presented in most MHC-II haplotypes, 
and this over-presentation seems even more pronounced than for MHC-I.

This over-presentation can be explained by the hydrophobicity of the MHC-I binding cleft.
\richel{
  Elaborate.
  See \url{https://github.com/richelbilderbeek/bbbq_article/issues/192}
}
Similar to our previous results with MHC-I, we predicted that the extent to which TMH-derived
epitopes are presented by each MHC-II haplotype is similar for the human, bacterial and viral proteome.

@@

To verify if the previous and the current method give rise to
notable difference, we show a side-by-side comparison
in figures \ref{fig:bianch_et_al_2017_1a} and \ref{fig:bilderbeek_et_al_2021_1a}.
The figures that haplotypes that over-present or under-present TMH-derived epitopes,
do so in both studies. The extent to which TMH-derived epitopes are
presented, however, is more extreme in our current setup.
